\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-12 smurf_paper.tex
mention jackknives in conclusions

The main problem with the iterative solution is divergence on large
angular scales, due to the degeneracy between the map, and the
low-frequency signal components that are removed. A simple strategy of
constraining empty regions of the map to zero (using either a
user-supplied mask for known sources, or an iterative determination of
signal above some \snr\ threshold) provides good constraints for both
compact objects, and bright/extended structures, allowing us to
effectively recover angular scales up to the order of the array
footprint (approximately 5\,arcmin).

For maps of faint point sources, a single (non-iterative) high-pass
filter at the start of the reduction produces maps that are nearly
white-noise limited. Residual large-scale noise can be removed with a
whitening filter, and sources detected using a matched-filter
(smoothing with the effective filtered point spread function).

@@

One regime in which SMURF does not presently perform well is in maps
of faint extended structures, since the zero-masking technique we have
adopted cannot be used. Since SMURF is both highly configurable and
extensible, it may be possible to develop an improved data model
and/or map constraint to assist in these situations, as more
experience with the instrument is gained. However, provided sufficient
computing power is available, the best solution in the long-term will
likely be a maximum-likelihood algorithm, such as SANEPIC
\citep{patanchon2008}. Even in this case, the existing iterative
solution from SMURF will probably be used as an initial step, since it
can quickly clean the bolometer time-series, as well as perform
map-based despiking (a necessarily iterative procedure).

>>>>

We have found that the iterative solution tends to diverge on large
angular scales due to the degeneracy between the map, and the
low-frequency signal components that are removed. A simple strategy of
constraining empty regions of the map to zero (using either a
user-supplied mask for known sources, or an iterative determination of
signal above some \snr\ threshold) provides good constraints for both
compact objects, and bright/extended structures. Particularly in the
latter case, using a combination of synthetic sources and an empirical
measurement of the map noise from jackknife tests (differences of
independent portions of the data), we have demonstrated that we can
effectively recover angular scales up to the order of the array
footprint (approximately 5\,arcmin).

For maps of faint point sources, a single (non-iterative) high-pass
filter at the start of the reduction produces maps that are nearly
white-noise limited. Residual large-scale noise can be removed with a
whitening filter (also established from jackknife estimates of the
noise), and sources detected using a matched-filter (smoothing with
the effective filtered point spread function).

@@

One regime in which SMURF does not presently perform well is in maps
of faint extended structures, since the zero-masking technique we have
adopted cannot be used. Since SMURF is both highly configurable and
extensible, it may be possible to develop an improved data model
and/or map constraint to assist in these situations, as more
experience with the instrument is gained. However, provided sufficient
computing power is available, the best solution in the long-term will
be a maximum-likelihood algorithm, such as SANEPIC
\citep{patanchon2008}. Even in this case, the existing iterative
solution from SMURF will probably be used as an initial step, since it
can quickly clean the bolometer time-series, as well as perform
map-based despiking (a necessarily iterative procedure).
